---
title: "Facets"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(ggplot2)
library(dplyr)
library(tidyr)
knitr::opts_chunk$set(echo = FALSE)
ecom <- readr::read_csv('https://raw.githubusercontent.com/rsquaredacademy/datasets/master/web.csv')
```

## Introduction

## Data

### Introduction

<hr>

```{r import, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Data'}
ecom
```

### Data Dictionary

<hr>

- id: row id
- referrer: referrer website/search engine
- os: operating system
- browser: browser
- device: device used to visit the website
- n_pages: number of pages visited
- duration: time spent on the website (in seconds)
- repeat: frequency of visits
- country: country of origin
- purchase: whether visitor purchased
- order_value: order value of visitor (in dollars)

## Grid

### Introduction

<hr>

Generate subplots that each display one subset of the data using

- `facet_grid()`
- `facet_wrap()`

## Grid - Columns

### Introduction

<hr>

### Example

<hr>

```{r facet1eg, echo=TRUE, collapse=FALSE, fig.align='center'}
ggplot(ecom, aes(n_pages, duration)) + 
  geom_point() +
  facet_grid(. ~ device)
```

### Instructions

<hr>

```{r facet1, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Columns'}
ggplot(ecom, aes(n_pages, duration)) + 
  geom_point() +
  facet_grid(. ~ device)
```

```{r facet1-solution}
ggplot(ecom, aes(n_pages, duration)) + 
  geom_point() +
  facet_grid(. ~ device)
```

## Grid - Rows

### Introduction

<hr>

### Example

<hr>

```{r facet2eg, echo=TRUE, collapse=FALSE, fig.align='center'}
ggplot(ecom, aes(n_pages, duration)) + 
  geom_point() +
  facet_grid(device ~ .)
```

### Instructions

<hr>

```{r facet2, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Rows'}
ggplot(ecom, aes(n_pages, duration)) + 
  geom_point() +
  facet_grid(device ~ .)
```

```{r facet2-solution}
ggplot(ecom, aes(n_pages, duration)) + 
  geom_point() +
  facet_grid(device ~ .)
```

## Grid - Rows & Columns

### Introduction

<hr>

### Example

<hr>

```{r facet3eg, echo=TRUE, collapse=FALSE, fig.align='center'}
ggplot(ecom, aes(n_pages, duration)) + 
  geom_point() +
  facet_grid(purchase ~ device)
```

### Instructions

<hr>

```{r facet3, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Rows & Columns'}
ggplot(ecom, aes(n_pages, duration)) + 
  geom_point() +
  facet_grid(purchase ~ device)
```

```{r facet3-solution}
ggplot(ecom, aes(n_pages, duration)) + 
  geom_point() +
  facet_grid(purchase ~ device)
```

## Grid - Rows & Columns

### Introduction

<hr>

### Example

<hr>

```{r facet4eg, echo=TRUE, collapse=FALSE, fig.align='center'}
ggplot(ecom, aes(n_pages, duration)) + 
  geom_point() +
  facet_grid(device ~ purchase)
```

### Instructions

<hr>

```{r facet4, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Rows & Columns'}
ggplot(ecom, aes(n_pages, duration)) + 
  geom_point() +
  facet_grid(device ~ purchase)
```

```{r facet4-solution}
ggplot(ecom, aes(n_pages, duration)) + 
  geom_point() +
  facet_grid(device ~ purchase)
```

## Grid - Scales

### Introduction

<hr>

### Example

<hr>

```{r facet5eg, echo=TRUE, collapse=FALSE, fig.align='center'}
ggplot(ecom, aes(n_pages, duration, color = factor(device))) +
  geom_point() + 
  facet_grid(. ~ device, scales = "free")
```

### Instructions

<hr>

Different range instead of fixed range.

```{r facet5, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Scales'}
ggplot(ecom, aes(n_pages, duration, color = factor(device))) +
  geom_point() + 
  facet_grid(. ~ device, scales = "free")
```

```{r facet5-solution}
ggplot(ecom, aes(n_pages, duration, color = factor(device))) +
  geom_point() + 
  facet_grid(. ~ device, scales = "free")
```

## Grid - Switch Axis

### Introduction

<hr>

### Example

<hr>

```{r facet6eg, echo=TRUE, collapse=FALSE, fig.align='center'}
ggplot(ecom, aes(n_pages, duration)) + 
  geom_point() + 
  facet_grid(device ~ purchase, switch = "both") 
```

### Instructions

<hr>

```{r facet6, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Switch Axis'}
ggplot(ecom, aes(n_pages, duration)) + 
  geom_point() + 
  facet_grid(device ~ purchase, switch = "both") 
```

```{r facet6-solution}
ggplot(ecom, aes(n_pages, duration)) + 
  geom_point() + 
  facet_grid(device ~ purchase, switch = "both") 
```

## Wrap

### Introduction

<hr>

```{r facet7, echo=TRUE, collapse=FALSE, fig.align='center'}
ggplot(ecom, aes(n_pages, duration)) +
  geom_point() +
  facet_wrap(~device)
```

## Wrap - Specify Rows

### Introduction

<hr>

### Example

<hr>

```{r facet8eg, echo=TRUE, collapse=FALSE, fig.align='center'}
ggplot(ecom, aes(n_pages, duration)) +
  geom_point() +
  facet_wrap(~device, nrow = 2)
```

### Instructions

<hr>

```{r facet8, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Specify Rows'}
ggplot(ecom, aes(n_pages, duration)) +
  geom_point() +
  facet_wrap(~device, nrow = 2)
```

```{r facet8-solution}
ggplot(ecom, aes(n_pages, duration)) +
  geom_point() +
  facet_wrap(~device, nrow = 3)
```

## Wrap - Rows & Columns

### Introduction

<hr>

### Example

<hr>

```{r facet10eg, echo=TRUE, collapse=FALSE, fig.align='center'}
ggplot(ecom, aes(n_pages, duration)) +
  geom_point() +
  facet_wrap(~device + purchase)
```

### Instructions

<hr>

```{r facet10, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Rows & Columns'}
ggplot(ecom, aes(n_pages, duration)) +
  geom_point() +
  facet_wrap(~device + purchase)
```

```{r facet10-solution}
ggplot(ecom, aes(n_pages, duration)) +
  geom_point() +
  facet_wrap(~device + purchase)
```

## Wrap - Rows & Columns

### Introduction

<hr>

### Example

<hr>

```{r facet11eg, echo=TRUE, collapse=FALSE, fig.align='center'}
ggplot(ecom, aes(n_pages, duration)) +
  geom_point() +
  facet_wrap(c("device", "purchase"))
```

### Instructions

<hr>

```{r facet11, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Rows & Columns'}
ggplot(ecom, aes(n_pages, duration)) +
  geom_point() +
  facet_wrap(c("device", "purchase"))
```

```{r facet11-solution}
ggplot(ecom, aes(n_pages, duration)) +
  geom_point() +
  facet_wrap(c("device", "purchase"))
```

## Wrap - Scales

### Introduction

<hr>

### Example

<hr>

```{r facet12eg, echo=TRUE, collapse=FALSE, fig.align='center'}
ggplot(ecom, aes(n_pages, duration)) +
  geom_point() +
  facet_wrap(~device, scales = "free")
```

### Instructions

<hr>

```{r facet12, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Scales'}
ggplot(ecom, aes(n_pages, duration)) +
  geom_point() +
  facet_wrap(~device, scales = "free")
```

```{r facet12-solution}
ggplot(ecom, aes(n_pages, duration)) +
  geom_point() +
  facet_wrap(~device, scales = "free")
```

