---
title: "Intro to SQL - Part 3"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(dbplyr)
library(dplyr)
library(DBI)
library(RSQLite)
knitr::opts_chunk$set(echo = FALSE)
ecom <- readr::read_csv('https://raw.githubusercontent.com/rsquaredacademy/datasets/master/web.csv')
con <- DBI::dbConnect(RSQLite::SQLite(), ":memory:")
copy_to(con, ecom)
```

## Introduction

## Aggregate Functions

Often, you will want to perform some calculation on the data in a database. SQL provides a few functions, called aggregate functions, to help you out with this.

For example,

`
SELECT AVG(budget)
FROM films`

gives you the average value from the budget column of the films table. Similarly, the MAX function returns the highest budget:

`
SELECT MAX(budget)
FROM films`

The SUM function returns the result of adding up the numeric values in a column:

`
SELECT SUM(budget)
FROM films`

## Aggregate - 1

You can probably guess what the MIN function does! Now it's your turn to try out some SQL functions.

```{r sql1, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'SUM'}
dbGetQuery(con, "SELECT SUM(n_visit) FROM ecom")
```

```{r sql2, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'AVG'}
dbGetQuery(con, "SELECT AVG(n_visit) FROM ecom")
```

```{r sql3, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'MAX'}
dbGetQuery(con, "SELECT MAX(n_visit) FROM ecom")
```

```{r sql4, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'MIN'}
dbGetQuery(con, "SELECT MIN(n_visit) FROM ecom")
```

## Aggregate - 2

You can probably guess what the MIN function does! Now it's your turn to try out some SQL functions.

```{r sql5, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'SUM'}
dbGetQuery(con, "SELECT SUM(n_visit) FROM ecom WHERE n_visit > 5")
```

```{r sql6, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'AVG'}
dbGetQuery(con, "SELECT AVG(n_visit) FROM ecom WHERE country LIKE 'P%'")
```

```{r sql7, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'MAX'}
dbGetQuery(con, "SELECT MAX(n_visit) FROM ecom WHERE device == 'tablet'")
```

```{r sql8, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'MIN'}
dbGetQuery(con, "SELECT MIN(n_visit) FROM ecom WHERE duration BETWEEN 600 AND 900")
```

## Alias - Part 1

You may have noticed in the first exercise of this chapter that the column name of your result was just the name of the function you used. For example,

`
SELECT MAX(budget)
FROM films`

gives you a result with one column, named max. But what if you use two functions like this?

`
SELECT MAX(budget), MAX(duration)
FROM films`

Well, then you'd have two columns named max, which isn't very useful!

To avoid situations like this, SQL allows you to do something called aliasing. Aliasing simply means you assign a temporary name to something. To alias, you use the AS keyword, which you've already seen earlier in this course.

For example, in the above example we could use aliases to make the result clearer:

`
SELECT MAX(budget) AS max_budget,
       MAX(duration) AS max_duration
FROM films`

Aliases are helpful for making results more readable!

## Alias - Part 2

```{r sql9, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Alias'}
dbGetQuery(con, "SELECT AVG(n_visit) AS avg_mobile FROM ecom WHERE device == 'mobile'")
```

```{r sql10, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Alias'}
dbGetQuery(con, "SELECT MAX(n_visit) AS max_visit FROM ecom")
```

```{r sql11, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Alias'}
dbGetQuery(con, "SELECT MIN(duration) AS min_duration FROM ecom")
```

