---
title: "ggplot2: Geoms"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(ggplot2)
library(dplyr)
knitr::opts_chunk$set(echo = FALSE)
ecom <- readr::read_csv('https://raw.githubusercontent.com/rsquaredacademy/datasets/master/web.csv')
gdp <- readr::read_csv('https://raw.githubusercontent.com/rsquaredacademy/datasets/master/gdp.csv')
```

## Agenda

<hr>

Create some of the most routinely used plots to explore data using the `geom_*` functions:

- Scatter Plot
- Bar Plot
- Box Plot
- Histogram
- Line Chart
- Regression Line


## Introduction


## Data

### Introduction

<hr>

```{r use, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Data'}
ecom
```

### Data Dictionary

<hr>

- id: row id
- referrer: referrer website/search engine
- os: operating system
- browser: browser
- device: device used to visit the website
- n_pages: number of pages visited
- duration: time spent on the website (in seconds)
- repeat: frequency of visits
- country: country of origin
- purchase: whether visitor purchased
- order_value: order value of visitor (in dollars)


## Point

### Introduction

<hr>

A scatter plot displays the relationship between two continuous variables. In ggplot2, we can build a scatter plot using `geom_point()`. Scatterplots can show you visually 

- the strength of the relationship between the variables 
- the direction of the relationship between the variables 
- and whether outliers exist

### Example

<hr>

```{r geoms2eg, echo=TRUE, collapse=FALSE, fig.align='center'}
ggplot(mtcars, aes(x = disp, y = mpg)) +
  geom_point()
```

### Instructions

<hr>

- set `x` to `wt`
- set `y` to `mpg`
- create a scatter plot by representing the data using points

```{r geoms2, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Point'}
ggplot(mtcars, aes(x = , y = )) + 
  
```

```{r geoms2-solution}
ggplot(mtcars, aes(x = wt, y = mpg)) + 
  geom_point()
```

## Bar 

### Introduction

<hr>

Bar plots present grouped data with rectangular bars. The bars may represent the frequency of the groups or values. Bar plots can be: 

- horizontal 
- vertical
- grouped
- stacked 
- proportional

### Example

<hr>

```{r geoms8eg, echo=TRUE, collapse=FALSE, fig.align='center'}
ggplot(mtcars, aes(x = cyl)) +
  geom_bar()
```

### Instructions

<hr>

- set `x` to `device`
- represent the data using bars

```{r geoms8, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Frequency'}
ggplot(ecom, aes(x = factor())) +
  
```

```{r geoms8-solution}
ggplot(ecom, aes(x = factor(device))) +
  geom_bar()
```

## Boxplot

### Introduction

<hr>

- examine the distribution of a variable  
- detect outliers, boxplots are very handy

### Example

<hr>

```{r geoms13eg, echo=TRUE, collapse=FALSE, fig.align='center'}
ggplot(mtcars, aes(x = factor(cyl), y = mpg)) +
  geom_boxplot()
```

### Instructions

<hr>

- set `x` to `device`
- set `y` to `n_pages`
- represent the data using a `boxplot`

```{r geoms13, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Box Plot'}
ggplot(ecom, aes(x = factor(), y = )) +
  
```

```{r geoms13-solution}
ggplot(ecom, aes(x = factor(device), y = n_pages)) +
  geom_boxplot()
```

## Histogram - Part 1

### Introduction

<hr>

Histograms are used to examine:

- distribution of a continuous variable
- skewness and kurtosis

### Example

<hr>

```{r geoms15eg, echo=TRUE, collapse=FALSE, fig.align='center'}
ggplot(mtcars, aes(x = mpg)) +
  geom_histogram()
```

### Instructions

<hr>

- set `x` to `duration`
- represent the data using a histogram

```{r geoms15, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Histogram'}
ggplot(ecom, aes(x = )) +
  
```

```{r geoms15-solution}
ggplot(ecom, aes(x = duration)) +
  geom_histogram()
```

## Histogram - Part 2

### Bins

<hr>

### Example

<hr>

```{r geoms16eg, echo=TRUE, collapse=FALSE, fig.align='center'}
ggplot(mtcars, aes(x = mpg)) +
  geom_histogram(bins = 5)
```

### Instructions

<hr>

- set `x` to `duration`
- represent the data using a histogram
- set the number of bins to 5

```{r geoms16, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Histogram Bins'}
ggplot(ecom, aes(x = )) +
  
```

```{r geoms16-solution}
ggplot(ecom, aes(x = duration)) +
  geom_histogram(bins = 5)
```

## Line - Part 1

### Introduction

<hr>

Line charts are used to examine trends over time.


### Data

<hr>

```{r import2, , exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Data'}
gdp
```

### Example

<hr>

```{r geomslineeg, echo=TRUE, collapse=FALSE, fig.align='center'}
ggplot(gdp, aes(year, china)) +
  geom_line()
```

## Line - Part 2

### Instructions

<hr>

- set `x` to `year`
- set `y` to `india`
- represent the data using a line 

```{r geomline1, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Line Chart'}
ggplot(gdp, aes(x = ___, y = ___ )) +
 
```

```{r geomline1-solution}
ggplot(gdp, aes(year, india)) +
  geom_line()
```

## Label

<hr>

### Instructions

<hr>


```{r geoms20, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Label'}
ggplot(mtcars, aes(disp, mpg, label = rownames(mtcars))) +
  geom_label()
```

## Text

### Introduction

<hr>

### Instructions

<hr>

```{r geoms19, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Text'}
ggplot(mtcars, aes(disp, mpg, label = rownames(mtcars))) +
  geom_text()
```

