---
title: "qplot"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(ggplot2)
knitr::opts_chunk$set(echo = FALSE)
```

## Agenda

<hr>

Learn to quickly build a set of plots that are routinely used to explore data:

- Scatter Plot
- Bar Plot
- Box Plot
- Line Chart
- Histogram

## Introduction

<hr>

Shortcut designed for those familiar with base plots. You can quickly produce a number of different
types of plots. Below are the key arguments:

- `x`    : data for X axis
- `y`    : data for Y axis
- `data` : a data frame or a tibble
- `geom` : symbols to represent data
- `fill` : color for filled symbols
- `color`: color for other symbols
- `shape`: shape of the geom
- `size` : size of the symbol

## Scatter Plot - Part 1

### Introduction

<hr>

### Example

<hr>

```{r gg2eg, echo=TRUE, collapse=FALSE, fig.align='center'}
qplot(x = hp, y = mpg, data = mtcars)
```

### Instructions

<hr>

- map `x` to `disp`
- map `y` to `mpg`
- map `data` to `mtcars`

```{r gg2, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Scatter Plot'}
# scatter plot using qplot
qplot(x = ___, y = ___, data = ___)
```

```{r gg2-solution}
qplot(x = disp, y = mpg, data = mtcars)
```

## Scatter Plot - Part 2

### Point & Line

<hr>

### Example

<hr>

```{r gg3eg, echo=TRUE, collapse=FALSE, fig.align='center'}
qplot(hp, mpg, data = mtcars, geom = c('point', 'line'))
```

### Instructions

<hr>

- map `geom` to `point` and `line`

```{r gg3, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Point & Line'}
qplot(disp, mpg, data = mtcars, geom = c('____', '____'))
```

```{r gg3-solution}
qplot(x = disp, y = mpg, data = mtcars, geom = c('point', 'line'))
```


## Scatter Plot - Part 3

### Color

<hr>

### Example

<hr>

```{r gg4eg, echo=TRUE, collapse=FALSE, fig.align='center'}
qplot(hp, mpg, data = mtcars, color = gear)
```

### Instructions

<hr>

- map `color` to `cyl`

```{r gg4, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Point Color'}
qplot(disp, mpg, data = mtcars, color = ____)
```

```{r gg4-solution}
qplot(x = disp, y = mpg, data = mtcars, color = 'cyl')
```

## Bar Plot - Part 1

### Introduction

<hr>

### Example

<hr>

```{r gg7eg, echo=TRUE, collapse=FALSE, fig.align='center'}
qplot(x = gear, data = mtcars, geom = c('bar'))
```

### Instructions

<hr>

- map `x` to `cyl`
- map `geom` to `bar`

```{r gg7, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Bar Plot'}
qplot(x = ____, data = mtcars, geom = c('____'))
```

```{r gg7-solution}
qplot(x = cyl, data = mtcars, geom = 'bar')
```


## Bar Plot - Part 2

### Color

<hr>

### Example

<hr>

```{r gg8eg, echo=TRUE, collapse=FALSE, fig.align='center'}
qplot(x = gear, data = mtcars, geom = c('bar'), fill = vs)
```

### Instructions

<hr>

- map `x` to `cyl`
- map `fill` to `am`

```{r gg8, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Color'}
qplot(x = ____, data = mtcars, geom = c('bar'), fill = ____)
```

```{r gg8-solution}
qplot(x = cyl, data = mtcars, geom = c('bar'), fill = am)
```


## Box Plot

### Introduction

<hr>

### Example

<hr>

```{r gg9eg, echo=TRUE, collapse=FALSE, fig.align='center'}
qplot(x = cyl, y = disp, data = mtcars, geom = c('boxplot'))
```

### Instructions

<hr>

- map `x` to `gear`
- map `y` to `mpg`
- map `geom` to `boxplot`


```{r gg9, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Box Plot'}
qplot(x = ____, y = ____, data = mtcars, geom = c('______'))
```

```{r gg9-solution}
qplot(x = gear, y = mpg, data = mtcars, geom = 'boxplot')
```

## Line Chart

### Introduction

<hr>

### Example

<hr>

```{r gg12eg, echo=TRUE, eval=FALSE, collapse=FALSE, fig.align='center'}
qplot(x = ____, y = ____, data = economics, geom = c('____'))
```

### Instructions

<hr>

- map `x` to `date`
- map `y` to `umemploy`
- map `geom` to `line`

```{r gg12, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Line Chart'}
qplot(x = ____, y = ____, data = economics, geom = c('____'))
```

```{r gg12-solution}
qplot(x = date, y = unemploy, data = economics, geom = c('line'))
```

## Histogram

### Introduction

<hr>

### Example

<hr>

```{r gg14eg, echo=TRUE, eval=FALSE, collapse=FALSE, fig.align='center'}
qplot(x = disp, data = mtcars, bins = 6)
```

### Instructions

<hr>

- map `x` to `mpg`
- set `bins` to 5

```{r gg14, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Histogram'}
qplot(x = ____, data = mtcars, bins = ____)
```

```{r gg14-solution}
qplot(x = mpg, data = mtcars, bins = 5)
```
