---
title: "ggplot2: Axis & Plot Labels"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(ggplot2)
library(dplyr)
library(tidyr)
knitr::opts_chunk$set(echo = FALSE)
```

## Agenda

<hr>

- add title and subtitle to the plot
- modify axis labels
- modify axis range
- remove axis
- format axis

To format the title or the axis labels, we have to modify the theme of the plot using the `theme()` function.
We can modify: 

- color
- font family
- font face
- font size 
- horizontal alignment 
- and angle


## Introduction

<hr>

## Title & Subtitle

<hr>

There are two ways to add title to a plot:

- `ggtitle()`
- `labs()`

Let us explore the `ggtitle()` function first. It takes two arguments:

- `label`: title of the plot
- `subtitle`: subtitle of the plot

### Example

<hr>

```{r axis3eg, echo=TRUE, collapse=FALSE, fig.align='center'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg)) +
  ggtitle(label = 'Plot Title', subtitle = 'Plot Subtitle')
```

### Instructions

<hr>

- set `label` to 'Displacement vs Miles Per Gallon'
- set `subtitle` to 'disp vs mpg'

```{r axis3, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Title & Subtitle'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg)) +
  ggtitle(___________)
```

```{r axis3-solution}
ggplot(mtcars) +
  geom_point(aes(disp, mpg)) +
  ggtitle(label = 'Displacement vs Mileage', subtitle = 'disp vs mpg')
```


## Axis Labels

<hr>

You can add labels to the axis using:

- `xlab()`
- `ylab()`
- `labs()`

### Example

<hr>

```{r axis4eg, echo=TRUE, collapse=FALSE, fig.align='center'}
ggplot(mtcars) +
  geom_point(aes(disp, hp)) +
  xlab('Displacement') + ylab('Horsepower')
```

### Instructions

<hr>

```{r axis4, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Axis Labels'}
# add X and Y axis labels
ggplot(mtcars) +
  geom_point(aes(disp, mpg)) 
```

```{r axis4-solution}
ggplot(mtcars) +
  geom_point(aes(disp, mpg)) +
  xlab('Displacement') + ylab('Miles Per Gallon')
```

## Labs

<hr>

The `labs()` function can be used to add the following to a plot:

- title
- subtitle
- X axis label
- Y axis label

### Example

<hr>

```{r axis5eg, echo=TRUE, collapse=FALSE, fig.align='center'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg)) +
  labs(title = 'Plot Title', subtitle = 'Subtitle', 
    x = 'X Axis Title', y = 'Y Axis Title')
```

### Instructions

<hr>

```{r axis5, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Axis Labels'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg)) +
  labs(___________)
```

```{r axis5-solution}
ggplot(mtcars) +
  geom_point(aes(disp, mpg)) +
  labs(title = 'Displacement vs Mileage', subtitle = 'disp vs mpg', 
    x = 'Displacement', y = 'Miles Per Gallon')
```


## Axis Range - Part 1

### Introduction

<hr>

In certain scenarios, you may want to modify the range of the axis. In ggplot2, we can achieve this using:

- `xlim()`
- `ylim()`
- `expand_limits()`


- `xlim()` and `ylim()` take a numeric vector of length 2 as input

### Example

<hr>

```{r axis6eg, echo=TRUE, collapse=FALSE, fig.align='center'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg)) +
  xlim(c(0, 600)) + ylim(c(0, 40))
```

### Instructions

<hr>

```{r axis6, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'X Axis Range'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg)) 
```

```{r axis6-solution}
ggplot(mtcars) +
  geom_point(aes(disp, mpg)) +
  xlim(c(0, 600)) +
  ylim(c(0, 40))
```

## Axis Range - Part 2

### Introduction

<hr>

`expand_limits()` takes two numeric vectors (each of length 2), one for each axis.

### Example

<hr>

```{r axis6aeg, echo=TRUE, collapse=FALSE, fig.align='center'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg)) +
  expand_limits(x = c(0, 600), y = c(0, 40))
```

### Instructions

<hr>

```{r axis6a, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'X Axis Range'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg)) 
```

```{r axis6a-solution}
ggplot(mtcars) +
  geom_point(aes(disp, mpg)) +
  expand_limits(x = c(0, 600), y = c(0, 40))
```


## Remove Axis Labels

<hr>

If you want to remove the axis labels all together, use the `theme()` function. It allows us to modify every aspect of the theme of the plot. Within `theme()`, set the following to `element_blank()`.

- `axis.title.x`
- `axis.title.y`

### Example

<hr>

```{r axis9eg, echo=TRUE, collapse=FALSE, fig.align='center'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg)) +
  theme(axis.title.x = element_blank(), axis.title.y = element_blank())
```

### Instructions

```{r axis9, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Remove Axis Labels'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg)) 
```

```{r axis9-solution}
ggplot(mtcars) +
  geom_point(aes(disp, mpg)) +
  theme(axis.title.x = element_blank(), axis.title.y = element_blank())
```

## Color & Font

<hr>

The font face can be any of the following:

- `plain` 
- `bold`
- `italic` 
- `bold.italic`

### Example

<hr>

```{r axis10eg, echo=TRUE, collapse=FALSE, fig.align='center'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg)) + ggtitle('Diaplacement vs Mileage') +
  theme(
    plot.title = element_text(
      color = 'blue', family = 'Arial', face = 'bold', size = 8
    )
  )
```

### Instructions

<hr>

```{r axis10, fig.align='center', message=FALSE, warning=FALSE, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Title Color'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg)) + ggtitle('Diaplacement vs Mileage') 
```

### Instructions

<hr>

```{r axis10a, fig.align='center', message=FALSE, warning=FALSE, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Title Color'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg)) + ggtitle('Diaplacement vs Mileage') 
```

### Instructions

<hr>

```{r axis10b, fig.align='center', message=FALSE, warning=FALSE, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Title Color'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg)) + ggtitle('Diaplacement vs Mileage') 
```

### Instructions

<hr>

```{r axis10c, fig.align='center', message=FALSE, warning=FALSE, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Title Color'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg)) + ggtitle('Diaplacement vs Mileage') 
```

```{r axis10-solution}
ggplot(mtcars) +
  geom_point(aes(disp, mpg)) + ggtitle('Diaplacement vs Mileage') +
  theme(plot.title = element_text(color = 'blue'))
```

```{r axis10a-solution}
ggplot(mtcars) +
  geom_point(aes(disp, mpg)) + ggtitle('Diaplacement vs Mileage') +
  theme(plot.title = element_text(family = 'Arial'))
```

```{r axis10b-solution}
ggplot(mtcars) +
  geom_point(aes(disp, mpg)) + ggtitle('Diaplacement vs Mileage') +
  theme(plot.title = element_text(face = 'bold'))
```

```{r axis10c-solution}
ggplot(mtcars) +
  geom_point(aes(disp, mpg)) + ggtitle('Diaplacement vs Mileage') +
  theme(plot.title = element_text(size = 8))
```


## Horizontal Alignment

### Introduction

<hr>

### Example

<hr>

```{r axis14eg, echo=TRUE, collapse=FALSE, fig.align='center'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg)) + ggtitle('Diaplacement vs Mileage') +
  theme(plot.title = element_text(hjust = 0.7))
```

### Instructions

<hr>

```{r axis14, fig.align='center', message=FALSE, warning=FALSE, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Title Alignment'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg)) + ggtitle('Diaplacement vs Mileage') 
```

```{r axis14-solution}
ggplot(mtcars) +
  geom_point(aes(disp, mpg)) + ggtitle('Diaplacement vs Mileage') +
  theme(plot.title = element_text(hjust = 0.3))
```


