---
title: "Box Plot"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(ggplot2)
library(dplyr)
library(tidyr)
knitr::opts_chunk$set(echo = FALSE)
ecom <- readr::read_csv('https://raw.githubusercontent.com/rsquaredacademy/datasets/master/web.csv')
```

## Introduction

### Agenda

<hr>

- build box plots
- modify box 
    - color
    - fill
    - alpha
    - line size
    - line type
- modify outlier 
    - color
    - shape 
    - size 
    - alpha

## Data

### Introduction

<hr>

```{r import, exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Data'}
ecom
```

### Data Dictionary

<hr>

- id: row id
- referrer: referrer website/search engine
- os: operating system
- browser: browser
- device: device used to visit the website
- n_pages: number of pages visited
- duration: time spent on the website (in seconds)
- repeat: frequency of visits
- country: country of origin
- purchase: whether visitor purchased
- order_value: order value of visitor (in dollars)

## Plot - Part 1

### Univariate Box Plot

<hr>

### Example

<hr>

```{r box2eg, echo=TRUE, collapse=FALSE, fig.align='center'}
ggplot(ecom) +
  geom_boxplot(aes(x = factor(1), y = n_visit))
```

### Instructions

<hr>

```{r box2, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Univariate Box Plot'}
ggplot(ecom) +
  geom_boxplot(aes(x = factor(1), y = n_visit))
```

```{r box2-solution}
ggplot(ecom) +
  geom_boxplot(aes(x = factor(1), y = n_visit))
```

## Plot - Part 2

### Introduction

<hr>

### Example

<hr>

```{r box3eg, echo=TRUE, collapse=FALSE, fig.align='center'}
ggplot(ecom) +
  geom_boxplot(aes(x = factor(device), y = n_visit))
```

### Instructions

<hr>

```{r box3, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Box Plot'}
ggplot(ecom) +
  geom_boxplot(aes(x = factor(device), y = n_visit))
```

```{r box3-solution}
ggplot(ecom) +
  geom_boxplot(aes(x = factor(device), y = n_visit))
```

## Horizontal Box Plot

### Introduction

<hr>

### Example

<hr>

```{r box4eg, echo=TRUE, collapse=FALSE, fig.align='center'}
ggplot(ecom) +
  geom_boxplot(aes(x = factor(device), y = n_visit)) +
  coord_flip()
```

### Instructions

<hr>

```{r box4, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Horizontal Box Plot'}
ggplot(ecom) +
  geom_boxplot(aes(x = factor(device), y = n_visit)) +
  coord_flip()
```

```{r box4-solution}
ggplot(ecom) +
  geom_boxplot(aes(x = factor(device), y = n_visit)) +
  coord_flip()
```

## Notch

### Introduction

<hr>

### Example

<hr>

```{r box5eg, echo=TRUE, collapse=FALSE, fig.align='center'}
ggplot(ecom) +
  geom_boxplot(aes(x = factor(device), y = n_visit),
               notch = TRUE) 
```

### Instructions

<hr>

```{r box5, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Notch'}
ggplot(ecom) +
  geom_boxplot(aes(x = factor(device), y = n_visit),
               notch = TRUE) 
```

```{r box5-solution}
ggplot(ecom) +
  geom_boxplot(aes(x = factor(device), y = n_visit),
               notch = TRUE) 
```

## Outliers - Introduction

### Introduction

<hr>

- color
- shape
- size
- alpha

## Outliers - Practice

### Instructions

<hr>

```{r box7, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Outlier Color'}
ggplot(ecom) +
  geom_boxplot(aes(x = factor(device), y = duration),
               outlier.color = 'red', outlier.shape = 23, outlier.size = 3)
```

```{r box7-solution}
ggplot(ecom) +
  geom_boxplot(aes(x = factor(device), y = duration),
               outlier.color = 'red', outlier.shape = 23, outlier.size = 3)
```

## Fill & Color

### Introduction

<hr>

## Fill & Color - Practice 1

### Instructions

<hr>

```{r box12, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Specify Values for Fill'}
ggplot(ecom) +
  geom_boxplot(aes(x = factor(device), y = duration),
               fill = c('blue', 'red', 'green')) 
```

```{r box12-solution}
ggplot(ecom) +
  geom_boxplot(aes(x = factor(device), y = duration),
               fill = c('blue', 'red', 'green')) 
```

## Fill & Color - Practice 2

### Instructions

<hr>

```{r box13, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Map Fill to Variable'}
ggplot(ecom) +
  geom_boxplot(aes(x = factor(device), y = duration,
               fill = factor(device))) 
```

```{r box13-solution}
ggplot(ecom) +
  geom_boxplot(aes(x = factor(device), y = duration,
               fill = factor(device))) 
```

## Fill & Color - Practice 3

### Instructions

<hr>

```{r box16, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Map Color to Variables'}
ggplot(ecom) +
  geom_boxplot(aes(x = factor(device), y = duration,
               color = factor(device))) 
```

```{r box16-solution}
ggplot(ecom) +
  geom_boxplot(aes(x = factor(device), y = duration,
               color = factor(device))) 
```