---
title: "Text Annotations"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(ggplot2)
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction

### Agenda

<hr>

- add custom text 
- modify color
- modify size
- modify fontface
- modify angle

## Overview

### Introduction

<hr>

Use `annotate()` to add custom text to a plot. It takes the following arguments:

- `geom`     : specify text
- `x`        : x axis location
- `y`        : y axis location
- `label`    : custom text 
- `color`    : color of text
- `size`     : size of text
- `fontface` : fontface of text
- `angle`    : angle of text

## Add Text

### Introduction

<hr>

### Example

<hr>

```{r ann2eg, echo=TRUE, collapse=FALSE, fig.align='center'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg)) +
  annotate('text', x = 200, y = 30, label = 'Sample Text')
```

### Instructions

<hr>

- add `'New Text'` to the plot
- set `x` coordinate to `300`
- set `y` coordinate to `40`

```{r ann2, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Add Text'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg)) +
  annotate('text', x = ___, y = ___, label = _______)



```

```{r ann2-solution}
ggplot(mtcars) +
  geom_point(aes(disp, mpg)) +
  annotate('text', x = 200, y = 30, label = 'New Text')
```

## Color

### Introduction

<hr>

### Example

<hr>

```{r ann4eg, echo=TRUE, collapse=FALSE, fig.align='center'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg)) +
  annotate('text', x = 200, y = 30, label = 'Sample Text', color = 'red')
```

### Instructions

<hr>

- add `'New Text'` to the plot
- set `x` coordinate to `300`
- set `y` coordinate to `40`
- set `color` to `'blue'`


```{r ann4, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Color'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg)) +
  annotate('text', x = ___, y = ___, label = _______, color = _____)
  


```

```{r ann4-solution}
ggplot(mtcars) +
  geom_point(aes(disp, mpg)) +
  annotate('text', x = 200, y = 30, label = 'Sample Text', color = 'blue')
```

## Size

### Introduction

<hr>

### Example

<hr>

```{r ann5eg, echo=TRUE, collapse=FALSE, fig.align='center'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg)) +
  annotate('text', x = 200, y = 30, label = 'Sample Text', size = 6)
```

### Instructions

<hr>

- add `'New Text'` to the plot
- set `x` coordinate to `300`
- set `y` coordinate to `40`
- set `size` to `9`


```{r ann5, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Size'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg)) +
  annotate('text', x = ___, y = ___, label = _______, size = ___)
```


```{r ann5-solution}
ggplot(mtcars) +
  geom_point(aes(disp, mpg)) +
  annotate('text', x = 200, y = 30, label = 'Sample Text', size = 9)
```

## Font

### Introduction

<hr>

### Example

<hr>

```{r ann6eg, echo=TRUE, collapse=FALSE, fig.align='center'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg)) +
  annotate('text', x = 200, y = 30, label = 'Sample Text', fontface = 'bold')
```

### Instructions

<hr>

- add `'New Text'` to the plot
- set `x` coordinate to `300`
- set `y` coordinate to `40`
- set `font` to `'italic'`

```{r ann6, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Font'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg)) +
  annotate('text', x = ___, y = ___, label = _______, fontface = ___)
```

```{r ann6-solution}
ggplot(mtcars) +
  geom_point(aes(disp, mpg)) +
  annotate('text', x = 200, y = 30, label = 'Sample Text', fontface = 'italic')
```

## Angle

### Introduction

<hr>

### Example

<hr>

```{r ann7eg, echo=TRUE, collapse=FALSE, fig.align='center'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg)) +
  annotate('text', x = 200, y = 30, label = 'Sample Text', angle = 25)
```

### Instructions

<hr>

- add `'New Text'` to the plot
- set `x` coordinate to `300`
- set `y` coordinate to `40`
- set `angle` to `'45'`

```{r ann7, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Angle'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg)) +
  annotate('text', x = ___, y = ___, label = _______, angle = ___)
```

```{r ann7-solution}
ggplot(mtcars) +
  geom_point(aes(disp, mpg)) +
  annotate('text', x = 200, y = 30, label = 'Sample Text', angle = 25)
```

## Summary

### Introduction

<hr>

### Instructions

<hr>

- set `label` to 'New Text'
- set `x` coordinate to `400`
- set `y` coordinate to `40`
- set `color` to `'green'`
- set `size` to `8`
- set `fontface` to `'bold'`
- set `angle` to `40`

```{r ann3, fig.align='center', exercise = TRUE, exercise.eval = FALSE, exercise.cap = 'Annotate'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg)) +
  annotate('text', x = __, y = ___, label = ___________,
           color = _____, size = ____, fontface = ____, angle = ___)
```

```{r ann3-solution}
ggplot(mtcars) +
  geom_point(aes(disp, mpg)) +
  annotate('text', x = 200, y = 30, label = 'New Text',
           color = 'green', size = 8, fontface = 'bold', angle = 40)
```